---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# PlottingTools

<!-- badges: start -->
<!-- badges: end -->

The goal of PlottingTools is to plot histograms for a given data attribute in a dataframe. The package simplifies the process of generating histograms for exploratory data analysis and reduce repeated code use.

## Installation

You can install the development version of PlottingTools like so:

```{r}

# install.packages("devtools")
devtools::install_github("https://github.com/stat545ubc-2023/assignment-b2-shycw1.git")

```

## Load the package
```{r}
library(PlottingTools)

```

## Example

Basic examples which shows you how to solve a common problem:


**CORRECT Usage 1** plot the histogram of radius_worst with default histogram bins

```{r correct-usage}

histogram_radius_worst <- plot_histogram(datateachr::cancer_sample, radius_worst)
print(histogram_radius_worst)

```


**CORRECT Usage 2** plot the histogram of radius_worst with specified histogram bins

```{r correct-usage-2}

histogram_radius_worst_100 <- plot_histogram(datateachr::cancer_sample, radius_worst, 100)
print(histogram_radius_worst_100)

```



**CORRECT Usage 3** plot the histogram of area_mean with specified histogram bins

```{r correct-usage-3}

histogram_area_mean <- plot_histogram(datateachr::cancer_sample, area_mean, 30)
print(histogram_area_mean)

```

